Pleiades: Interactive Composing Tools for Vega-Lite Charts

### 2019-06-12 final/paper/paper.tex
move poster and paper to final folder

Furthermore, when users design composite views, it makes sense for users to build
composite views starting from a unit spec. Then, they can add more views and is
able to experiment with the design by adding in and taking out views. With the
nature of JSON, however, when working with Vega-Lite, specification is created
from the outer most composite view and add inner views later. Additionally, when
users need to make changes to the layout of composite views, they have to make
changes to the JSON specification. With this, the users need to focus on how to
implement the JSON, which would distract the focus of the user on the design.

@@

Pleiades is built on top of Vega-Lite to further abstracts away the implementation
details of view composition using JSON. In this work, we assume that users already
are familiar with basic Vega-Lite that they are comfortable working with unit spec
using Vega-Lite. Having all the unit specs the users need to compose, users can use
Pleiades to compose them with the interactive GUI.

@@

\subsubsection{Place/Replace}
When the working area is empty, user can select a view in the sidebar. Then click
“PLACE” to place the view to the working area. When the working area is not empty,
the same button's text changes to ``REPLACE''.

>>>>

Furthermore, when users design composite views, it makes sense for users to build
composite views starting from a unit spec. Then, they can add more views and is
able to experiment with the design by adding in and taking out views. With the
nature of JSON, however, when working with Vega-Lite, specification is created
from the outermost composite view and add inner views later. Additionally, when
users need to make changes to the layout of composite views, they have to make
changes to the JSON specification. With this, the users need to focus on how to
implement the JSON, which would distract the focus of the user on the design.

@@

Pleiades is built on top of Vega-Lite to further abstract away the implementation
details of view composition using JSON. In this work, we assume that users are
already familiar with basic Vega-Lite that they are comfortable working with unit
spec using Vega-Lite. Having all the unit specs the users need to compose, users
can use Pleiades to compose them with the interactive GUI.

@@

\subsubsection{Place/Replace}
When the working area is empty, user can select a view in the sidebar. Then click
“PLACE” to place the view to the working area. When the working area is not empty,
the same button's text changes to ``REPLACE''. Users can click this button when
there are one selected view from the sidebar and one selected view from the working
area. Then, the selected view in the working area is replaced with the selceted
view in the sidebar.
